---
title: "NFL Stadiums"
subtitle: "An R Markdown Presentation. Hit the arrow key on your keyboard to continue."
author: "Jacob M. Lundeen"
date: "2023-03-21"
output: ioslides_presentation
---

```{r setup, include=FALSE, echo = FALSE, message = FALSE, warnings = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(geosphere)
library(leaflet)
library(gt)
```

```{r, results='hide'}
nflLatLong <- read.csv("NFLData.csv")
teamIcons <- icons(
  iconUrl = nflLatLong$Logos,
  iconWidth = 40*215/230, iconHeight = 31, iconAnchorX = 31*215/230/2,
  iconAnchorY = 16
  )
```

## Presentation Information

This presentation is done as a requirement for the Developing Data Products
course from Johns Hopkins University. The presentation is a series of slides
using the Leaflet package to show maps with markers of the 32 National Football
League stadiums. The markers, when both hovered over or clicked on, will
present information to the user about the stadiums. The user can also click on
the blue polygons for more information.

To progress through the presentation, use the arrow keys on the keyboard or
click to the right or left just outside the white slide box.

## National Football League Stadiums

```{r}
leaflet() %>%
  addTiles() %>%
  addMarkers(data = nflLatLong,
             lng = ~longitude,
             lat = ~latitude,
             clusterOptions = markerClusterOptions(),
             icon = teamIcons, 
             label = ~Team,
             popup = ~paste("<br>Conference:", Conference,
                            "<br>State:", State,
                            "<br>Number of SBs:", SBs)
             )
```

## National Football Conference Stadiums

```{r}
nfcSubset = subset(nflLatLong, Conference == "NFC")
nfcIcons <- icons(
  iconUrl = nfcSubset$Logos,
  iconWidth = 40*215/230, iconHeight = 31, iconAnchorX = 31*215/230/2,
  iconAnchorY = 16
)
leaflet() %>%
  addTiles() %>%
  addMarkers(data = nfcSubset,
             lng = ~longitude,
             lat = ~latitude,
             clusterOptions = markerClusterOptions(),
             icon = nfcIcons, 
             label = ~Team,
             popup = ~paste("<br>Conference:", Conference,
                            "<br>State:", State,
                            "<br>Number of SBs:", SBs)
             )
```

## NFC North Division Stadiums

```{r}
nfcNSubset = subset(nfcSubset, Division == "North")
nfcNIcons <- icons(
  iconUrl = nfcNSubset$Logos,
  iconWidth = 40*215/230, iconHeight = 31, iconAnchorX = 31*215/230/2,
  iconAnchorY = 16
)
nfcNortharea <- round(areaPolygon(as.matrix(nfcNSubset[,5:4])) * (3.861 * 10^(-7)), 2)
leaflet() %>%
  addTiles() %>%
  addPolygons(lng = nfcNSubset$longitude, lat = nfcNSubset$latitude, 
              popup = paste("Area:", nfcNortharea, "mi<sup>2")) %>%
  addMarkers(data = nfcNSubset,
             lng = ~longitude,
             lat = ~latitude,
             clusterOptions = markerClusterOptions(),
             icon = nfcNIcons, 
             label = ~Team,
             popup = ~paste("<br>Conference:", Conference,
                            "<br>State:", State,
                            "<br>Number of SBs:", SBs)
             )
```

## NFC South Division Stadiums

```{r}
nfcSSubset = subset(nfcSubset, Division == "South")
rownames(nfcSSubset)<-1:nrow(nfcSSubset)
nfcSSubset <- nfcSSubset[c(1,3,2,4),]
nfcSIcons <- icons(
  iconUrl = nfcSSubset$Logos,
  iconWidth = 40*215/230, iconHeight = 31, iconAnchorX = 31*215/230/2,
  iconAnchorY = 16
)
nfcSoutharea <- round(areaPolygon(as.matrix(nfcSSubset[,5:4])) * (3.861 * 10^(-7)), 2)
leaflet() %>%
  addTiles() %>%
  addPolygons(lng = nfcSSubset$longitude, lat = nfcSSubset$latitude, 
              popup = paste("Area:", nfcSoutharea, "mi<sup>2")) %>%
  addMarkers(data = nfcSSubset,
             lng = ~longitude,
             lat = ~latitude,
             clusterOptions = markerClusterOptions(),
             icon = nfcSIcons, 
             label = ~Team,
             popup = ~paste("<br>Conference:", Conference,
                            "<br>State:", State,
                            "<br>Number of SBs:", SBs)
             )
```

## NFC East Division Stadiums

```{r}
nfcESubset = subset(nfcSubset, Division == "East")
rownames(nfcESubset)<-1:nrow(nfcESubset)
nfcESubset <- nfcESubset[c(1,2,4,3),]
nfcEIcons <- icons(
  iconUrl = nfcESubset$Logos,
  iconWidth = 40*215/230, iconHeight = 31, iconAnchorX = 31*215/230/2,
  iconAnchorY = 16
)
nfcEastarea <- round(areaPolygon(as.matrix(nfcESubset[,5:4])) * (3.861 * 10^(-7)), 2)
leaflet() %>%
  addTiles() %>%
  addPolygons(lng = nfcESubset$longitude, lat = nfcESubset$latitude, 
              popup = paste("Area:", nfcEastarea, "mi<sup>2")) %>%
  addMarkers(data = nfcESubset,
             lng = ~longitude,
             lat = ~latitude,
             clusterOptions = markerClusterOptions(),
             icon = nfcEIcons, 
             label = ~Team,
             popup = ~paste("<br>Conference:", Conference,
                            "<br>State:", State,
                            "<br>Number of SBs:", SBs)
             )
```

## NFC West Division Stadiums

```{r}
nfcWSubset = subset(nfcSubset, Division == "West")
rownames(nfcWSubset)<-1:nrow(nfcWSubset)
nfcWSubset <- nfcWSubset[c(1,3,2,4),]
nfcWIcons <- icons(
  iconUrl = nfcWSubset$Logos,
  iconWidth = 40*215/230, iconHeight = 31, iconAnchorX = 31*215/230/2,
  iconAnchorY = 16
)
nfcWestarea <- round(areaPolygon(as.matrix(nfcWSubset[,5:4])) * (3.861 * 10^(-7)), 2)
leaflet() %>%
  addTiles() %>%
  addPolygons(lng = nfcWSubset$longitude, lat = nfcWSubset$latitude, 
              popup = paste("Area:", nfcWestarea, "mi<sup>2")) %>%
  addMarkers(data = nfcWSubset,
             lng = ~longitude,
             lat = ~latitude,
             clusterOptions = markerClusterOptions(),
             icon = nfcWIcons, 
             label = ~Team,
             popup = ~paste("<br>Conference:", Conference,
                            "<br>State:", State,
                            "<br>Number of SBs:", SBs)
             )
```

## American Football Conference Stadiums

```{r}
afcSubset = subset(nflLatLong, Conference == "AFC")
afcIcons <- icons(
  iconUrl = afcSubset$Logos,
  iconWidth = 40*215/230, iconHeight = 31, iconAnchorX = 31*215/230/2,
  iconAnchorY = 16
)
leaflet() %>%
  addTiles() %>%
  addMarkers(data = afcSubset,
             lng = ~longitude,
             lat = ~latitude,
             clusterOptions = markerClusterOptions(),
             icon = afcIcons, 
             label = ~Team,
             popup = ~paste("<br>Conference:", Conference,
                            "<br>State:", State,
                            "<br>Number of SBs:", SBs)
             )
```

## AFC North Division Stadiums

```{r}
afcNorthSubset = subset(afcSubset, Division == "North")
rownames(afcNorthSubset)<-1:nrow(afcNorthSubset)
afcNorthSubset <- afcNorthSubset[c(1,3,4,2),]
afcNorthIcons <- icons(
  iconUrl = afcNorthSubset$Logos,
  iconWidth = 40*215/230, iconHeight = 31, iconAnchorX = 31*215/230/2,
  iconAnchorY = 16
)
afcNorthArea <- round(areaPolygon(as.matrix(afcNorthSubset[,5:4])) * (3.861 * 10^(-7)), 2)
leaflet() %>%
  addTiles() %>%
  addPolygons(lng = afcNorthSubset$longitude, lat = afcNorthSubset$latitude, 
              popup = paste("Area:", afcNorthArea, "mi<sup>2")) %>%
  addMarkers(data = afcNorthSubset,
             lng = ~longitude,
             lat = ~latitude,
             clusterOptions = markerClusterOptions(),
             icon = afcNorthIcons, 
             label = ~Team,
             popup = ~paste("<br>Conference:", Conference,
                            "<br>State:", State,
                            "<br>Number of SBs:", SBs)
             )
```

## AFC South Division Stadiums

```{r}
afcSouthSubset = subset(afcSubset, Division == "South")
#rownames(nfcWSubset)<-1:nrow(afcNorthSubset)
#nfcWSubset <- nfcWSubset[c(1,3,2,4),]
afcSouthIcons <- icons(
  iconUrl = afcSouthSubset$Logos,
  iconWidth = 40*215/230, iconHeight = 31, iconAnchorX = 31*215/230/2,
  iconAnchorY = 16
)
afcSouthArea <- round(areaPolygon(as.matrix(afcSouthSubset[,5:4])) * (3.861 * 10^(-7)), 2)
leaflet() %>%
  addTiles() %>%
  addPolygons(lng = afcSouthSubset$longitude, lat = afcSouthSubset$latitude, 
              popup = paste("Area:", afcSouthArea, "mi<sup>2")) %>%
  addMarkers(data = afcSouthSubset,
             lng = ~longitude,
             lat = ~latitude,
             clusterOptions = markerClusterOptions(),
             icon = afcSouthIcons, 
             label = ~Team,
             popup = ~paste("<br>Conference:", Conference,
                            "<br>State:", State,
                            "<br>Number of SBs:", SBs)
             )
```

## AFC East Division Stadiums

```{r}
afcEastSubset = subset(afcSubset, Division == "East")
#rownames(nfcWSubset)<-1:nrow(afcNorthSubset)
#nfcWSubset <- nfcWSubset[c(1,3,2,4),]
afcEastIcons <- icons(
  iconUrl = afcEastSubset$Logos,
  iconWidth = 40*215/230, iconHeight = 31, iconAnchorX = 31*215/230/2,
  iconAnchorY = 16
)
afcEastArea <- round(areaPolygon(as.matrix(afcEastSubset[,5:4])) * (3.861 * 10^(-7)), 2)
leaflet() %>%
  addTiles() %>%
  addPolygons(lng = afcEastSubset$longitude, lat = afcEastSubset$latitude, 
              popup = paste("Area:", afcEastArea, "mi<sup>2")) %>%
  addMarkers(data = afcEastSubset,
             lng = ~longitude,
             lat = ~latitude,
             clusterOptions = markerClusterOptions(),
             icon = afcEastIcons, 
             label = ~Team,
             popup = ~paste("<br>Conference:", Conference,
                            "<br>State:", State,
                            "<br>Number of SBs:", SBs)
             )
```

## AFC West Division Stadiums

```{r}
afcWestSubset = subset(afcSubset, Division == "West")
rownames(afcWestSubset)<-1:nrow(afcWestSubset)
afcWestSubset <- afcWestSubset[c(1,4,2,3),]
afcWestIcons <- icons(
  iconUrl = afcWestSubset$Logos,
  iconWidth = 40*215/230, iconHeight = 31, iconAnchorX = 31*215/230/2,
  iconAnchorY = 16
)
afcWestArea <- round(areaPolygon(as.matrix(afcWestSubset[,5:4])) * (3.861 * 10^(-7)), 2)
leaflet() %>%
  addTiles() %>%
  addPolygons(lng = afcWestSubset$longitude, lat = afcWestSubset$latitude, 
              popup = paste("Area:", afcWestArea, "mi<sup>2")) %>%
  addMarkers(data = afcWestSubset,
             lng = ~longitude,
             lat = ~latitude,
             clusterOptions = markerClusterOptions(),
             icon = afcWestIcons, 
             label = ~Team,
             popup = ~paste("<br>Conference:", Conference,
                            "<br>State:", State,
                            "<br>Number of SBs:", SBs)
             )
```

## Summary Statistics

```{r, caption="Area is in squared miles"}
Division_Area <- c(nfcNortharea, nfcSoutharea, nfcEastarea, nfcWestarea, 
                   afcNorthArea, afcSouthArea, afcEastArea, afcWestArea)
Division_SBs <- c(sum(nfcNSubset$SBs), sum(nfcSSubset$SBs), sum(nfcESubset$SBs), sum(nfcWSubset$SBs),
                  sum(afcNorthSubset$SBs), sum(afcSouthSubset$SBs), sum(afcEastSubset$SBs), sum(afcEastSubset$SBs))
Divisions <- c("NFC_North", "NFC_South", "NFC_East", "NFC_West",
                          "AFC_North", "AFC_South", "AFC_East", "AFC_West")
summaryStats <- data.frame(Divisions, Division_Area, Division_SBs)



gt_tbl <- summaryStats %>%
  gt(rowname_col = 'Divisions')
gt_tbl <- gt_tbl %>%
  tab_header(
    title = "NFL Stadiums by Division",
    subtitle = "Area covered and number of Super Bowls"
  ) %>%
  cols_label(
    Division_Area = "Division Area",
    Division_SBs = "Super Bowls"
  ) %>%
  tab_footnote(
    footnote = "Division Area is in square milage"
  ) %>%
  tab_row_group(
    label = "NFC",
    rows = 1:4
  ) %>%
  tab_row_group(
    label = "AFC",
    rows = 5:8
  )
gt_tbl
```